### 2019-06-24 methodology/data-set.tex
sez 3.4 da controllare

\subsection{Provided data set}
The data set I was provided with consists of the histological records of 3218 breast cancer patients.
The data set had been pre-processed by collaborators of the ICT with some of the variables being compiled by hand. 
In Tab. \ref{tab:datasetvariables} is a description of the measured variables, together with their clinical meaning.

\begin{table*}[htbp]
\caption{Data set variables}
\begin{center}
\begin{tabular}{l l}
\hline \\
\textbf{Variable} & Meaning \\
\hline \\
\textbf{Codice globale} & Unique patient identifier \\
\textbf{mut17q21} & \\
\textbf{loss 17} & \\
\textbf{et\`a arrotondata} & The age of the patient at diagnosis\\
\textbf{Lateralit\`a} & The affected breast \\
\textbf{Situ SUBGROUP MZ} & The site code of the tumour \\
\textbf{Morfologia SUBGROUP MZ} & The morphology classification of the tumour \\
\textbf{pT SUBGROUP MZ} & Primary tumour in the TNM classification for breast cancer \\
\textbf{pN SUBGROUP MZ} & Pathologic in the TNM classification for breast cancer \\
\textbf{M 8.2.96} & Distant metastasis in the TNM classification for breast cancer \\
\textbf{Differenziazione} &  \\
\textbf{Recettori estrogeni percento 1.1.2003} & \\
\textbf{Recettori progestinici percento 1.1.2003} & \\
\textbf{c erbB 2  cod percento 1.1.2003} & \\
\textbf{Ki67 cod percento} & \\
\textbf{FISHRatio} & \\
\end{tabular}
\label{tab:datasetvariables}
\end{center}
\end{table*}

@@

\begin{table*}[htbp]
\caption{Data set variables}
\begin{center}
\begin{tabular}{l l}
\hline \\
\textbf{Variable} & Action \\
\hline \\
\textbf{Codice globale} & Leave untouched \\
\textbf{mut17q21} & Remove blanks \\
\textbf{loss 17} & Remove blanks \\
\textbf{eta arrotondata} & Bin into \enquote{$< 40$}, \enquote{$40-50$}, \enquote{$\geq 50$}\\
\textbf{lateralita} & Remove blanks and \enquote{sconosciuta} \\
\textbf{situ} & Remove blanks \\
\textbf{morfologia} & Remove blanks and \enquote{unuseful} if performance on classification is subpar \\
\textbf{pT} & Remove blanks and \enquote{unuseful}  \\
\textbf{pN} & Remove blanks and bin into \enquote{0} and \enquote{$\neq0$}\\
\textbf{M} & Remove blanks \\
\textbf{differenziazione} & Remove blanks and \enquote{Sconosciuto o non applicabile} \\
\textbf{recettori estrogeni} & Remove blanks and bin into \enquote{negativo} if $\leq 10$, \enquote{debolmente positivo} if $\leq 50$, \enquote{fortemente positivo} if $> 50$ \\
\textbf{recettori progestinici} & Remove blanks and bin into \enquote{negativo} if $\leq 10$, \enquote{debolmente positivo} if $\leq 50$, \enquote{fortemente positivo} if $> 50$ \\
\textbf{c erbB 2} & Remove blanks \\
\textbf{ki67} & Remove blanks and bin into \enquote{<14}, \enquote{14-20}, \enquote{20-30}, \enquote{>30} \\
\textbf{FISH} & Remove blanks \\
\end{tabular}
\label{tab:datasetpreprocess}
\end{center}
\end{table*}

what vittoria told me to do to clean, describe the data set

>>>>

\subsection{Provided data set}
The data set I was provided with consists of the histological records of 3218 breast cancer patients.
The data set had been pre-processed by collaborators of the ICT with some of the values being compiled by hand. 
In Tab. \ref{tab:datasetvariables} is a description of the measured variables, together with their clinical meaning.
The value distribution of the data set is shown in Tab. \ref{tab:datasetdistribution}.

@@

\begin{table*}[htbp]
\caption{Data set variables}
\begin{tabularx}{\textwidth}{@{} l Y @{}}
\toprule 
\textbf{Variable} & Meaning \\
\midrule 
\textbf{Codice globale} & Unique patient identifier \\
\textbf{mut17q21} & \\
\textbf{loss 17} & \\
\textbf{et\`a arrotondata} & The age of the patient at diagnosis\\
\textbf{Lateralit\`a} & The affected breast \\
\textbf{Situ SUBGROUP MZ} & The site code of the tumour \\
\textbf{Morfologia SUBGROUP MZ} & The morphology classification of the tumour \\
\textbf{pT SUBGROUP MZ} & Primary tumour in the TNM classification for breast cancer \\
\textbf{pN SUBGROUP MZ} & Pathologic in the TNM classification for breast cancer \\
\textbf{M 8.2.96} & Distant metastasis in the TNM classification for breast cancer \\
\textbf{Differenziazione} &  \\
\textbf{Recettori estrogeni percento 1.1.2003} & \\
\textbf{Recettori progestinici percento 1.1.2003} & \\
\textbf{c erbB 2  cod percento 1.1.2003} & \\
\textbf{Ki67 cod percento} & \\
\textbf{FISHRatio} & \\
\bottomrule
\end{tabularx}
\label{tab:datasetvariables}
\end{table*}

\begin{table*}[htbp]
\caption{Data set distribution}
\begin{tabularx}{\textwidth}{@{} l X c @{}}
\toprule 
\textbf{Variable} & Unique values & Distribution \\
\midrule 
\textbf{mut17q21} & 2 & \includegraphics[width=0.2\textwidth, height=10mm]{methodology/images/mut17q21}  \\
\textbf{loss 17} & 3 & \includegraphics[width=0.2\textwidth, height=10mm]{methodology/images/loss_17}\\
\textbf{eta arrotondata} & 74 & \includegraphics[width=0.2\textwidth, height=10mm]{methodology/images/eta_arrotondata}\\
\textbf{ateralit\`a} & 3 & \includegraphics[width=0.2\textwidth, height=10mm]{methodology/images/lateralita} \\
\textbf{situ} & 5 & \includegraphics[width=0.2\textwidth, height=10mm]{methodology/images/situ} \\
\textbf{morfologia} & 5 & \includegraphics[width=0.2\textwidth, height=10mm]{methodology/images/morfologia} \\
\textbf{pT} & 23 & \includegraphics[width=0.2\textwidth, height=10mm]{methodology/images/pt} \\
\textbf{pN} & 6 & \includegraphics[width=0.2\textwidth, height=10mm]{methodology/images/pn} \\
\textbf{M} & 3 & \includegraphics[width=0.2\textwidth, height=10mm]{methodology/images/m} \\
\textbf{differenziazione} & 5 & \includegraphics[width=0.2\textwidth, height=10mm]{methodology/images/differenziazione}  \\
\textbf{recettori estrogeni} & 40 & \includegraphics[width=0.2\textwidth, height=10mm]{methodology/images/recettori_estrogeni} \\
\textbf{recettori progestinici} & 40 & \includegraphics[width=0.2\textwidth, height=10mm]{methodology/images/recettori_progestinici}\\
\textbf{c erbB 2} & 4 & \includegraphics[width=0.2\textwidth, height=10mm]{methodology/images/c_erb_2}\\
\textbf{Ki67} & 52 & \includegraphics[width=0.2\textwidth, height=10mm]{methodology/images/ki67}\\
\textbf{FISH} & 5 & \includegraphics[width=0.2\textwidth, height=10mm]{methodology/images/fish}\\
\bottomrule
\end{tabularx}
\label{tab:datasetdistribution}
\end{table*}

\begin{table*}[htbp]
\caption{Data set preprocessing}
\begin{tabularx}{\textwidth}{@{} l Y @{}}
\toprule 
\textbf{Variable} & Action \\
\midrule 
\textbf{Codice globale} & Remove variable \\
\textbf{mut17q21} & Remove blanks \\
\textbf{loss 17} & Remove blanks \\
\textbf{eta arrotondata} & Bin into \enquote{$< 40$}, \enquote{$40-50$}, \enquote{$\geq 50$}\\
\textbf{lateralita} & Remove blanks and \enquote{sconosciuta} \\
\textbf{situ} & Remove blanks \\ \addlinespace
\textbf{morfologia} & Remove blanks and \enquote{unuseful} if performance on classification is subpar \\ \addlinespace
\textbf{pT} & Remove blanks and \enquote{unuseful}  \\
\textbf{pN} & Remove blanks and bin into \enquote{0} and \enquote{$\neq0$}\\
\textbf{M} & Remove blanks \\ 
\textbf{differenziazione} & Remove blanks and \enquote{Sconosciuto o non applicabile} \\ \addlinespace
\textbf{recettori estrogeni} & Remove blanks and bin into \enquote{negativo} if $\leq 10$,
		\enquote{debolmente positivo} if $\leq 50$, 
		\enquote{fortemente positivo} if $> 50$ \\ \addlinespace
\textbf{recettori progestinici} & Remove blanks and bin into \enquote{negativo} if $\leq 10$, 
		\enquote{debolmente positivo} if $\leq 50$, 
		\enquote{fortemente positivo} if $> 50$ \\ \addlinespace
\textbf{c erbB 2} & Remove blanks \\ 
\textbf{ki67} & Remove blanks and bin into \enquote{<14}, 
		\enquote{14-20}, \enquote{20-30}, \enquote{>30} \\ 
\textbf{FISH} & Remove blanks \\
\bottomrule
\end{tabularx}
\label{tab:datasetpreprocess}
\end{table*}
